other functionalities

### 2022-01-19 inst/gitbook/05_other-functionalities.Rmd
Manual update for v1.7 INIT
added MCMCglmm utilities in the manual

>>>>

## `MCMCglmm` utilities {#MCMCglmm-utilities}

Since version `1.7`, the `dispRity` package contains several utility functions for manipulating `"MCMCglmm"` (that is, objects returned by the function `MCMCglmm::MCMCglmm`).
These objects are a modification of the `mcmc` object (from the package `coda`) and can be sometimes cumbersome to manipulate because of the huge amount of data in it.
You can use the functions `MCMCglmm.traits` for extracting the number of traits, `MCMCglmm.levels` for extracting the level names, `MCMCglmm.sample` for sampling posterior IDs and `MCMCglmm.covars` for extracting variance-covariance matrices.

```{r}
## Loading the charadriiformes data that contains a MCMCglmm object
data(charadriiformes)]
my_MCMCglmm <- charadriiformes$posteriors

## Which traits where used in this model?
MCMCglmm.traits(my_MCMCglmm)

## Which levels where used for the model's random terms and/or residuals?
MCMCglmm.levels(my_MCMCglmm)

## The level names are converted for clarity but you can get them unconverted
## (i.e. as they appear in the model)
MCMCglmm.levels(my_MCMCglmm, convert = FALSE)

## Sampling 2 random posteriors samples IDs
(random_samples <- MCMCglmm.sample(my_MCMCglmm, n = 2))

## Extracting these two random amples
my_covars <- MCMCglmm.covars(my_MCMCglmm, sample = random_samples)
```

See more in the [`$covar` section](#covar) on what to do with these `"MCMCglmm"` objects.
